### 2016-07-09 MSSM.tex
changes, presumably mainly in Virt_Real chapter

As in the Standard Model this spontaneous symmetry breaking and the presence of Yukawa-terms (first three terms of eq. \eqref{eq:W_MSSM}) lead to masses of the fermions.\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance (see Appendix \ref{sec:2spinor_notation} for the definition of $\epsilon^{\alpha\beta}$).} Apart from that there are also other terms like quark-squark-higgsino interactions. In addition there is the $\mu$-term which is responsible for Higgsino and Higgs masses.\\

>>>>

As in the Standard Model this spontaneous symmetry breaking and the presence of Yukawa-terms (first three terms of eq. \eqref{eq:W_MSSM}) lead to masses of the fermions.\footnote{Note the sum convention of $SU_{\mathrm{L}}(2)$ doublets: $\hat{H}_u \hat{Q} =  (\hat{H}_u)_{\alpha}\hat{Q}_\beta \epsilon^{\alpha\beta}$ to ensure gauge invariance (see Appendix \ref{sec:2spinor_notation} for the definition of $\epsilon^{\alpha\beta}$). This convention was not used in the Standard Model.} Apart from that there are also other terms like quark-squark-higgsino interactions. In addition there is the $\mu$-term which is responsible for Higgsino and Higgs masses.\\

### 2016-07-09 NLO.tex
changes, presumably mainly in Virt_Real chapter

Now considers the full $(n+m)$-point function in scalar theory. One can decompose it into an amputated $(n+m)$-point function and "full" propagators like written in eq. \eqref{eq:propagator} and depicted in fig. \ref{fig:fullpropagator}.

@@

	\draw[fill=black] (80:1.5) circle (.01);
	\draw[fill=black] (90:1.5) circle (.01);
	\draw[fill=black] (100:1.5) circle (.01);
	\draw[fill=black] (-80:1.5) circle (.01);
	\draw[fill=black] (-90:1.5) circle (.01);
	\draw[fill=black] (-100:1.5) circle (.01);
\end{tikzpicture}
\caption{Diagrammatic figure of a "full" $(n+m)$-point function. Apart from the "full" propagators there is the "full" amputated $(n+m)$-point function}
\end{center}
\end{figure}\\
Inserting the expression
\begin{align}
\frac{i}{p^2 - m_0^2 - \Sigma(p^2)} \sim \frac{i Z}{p^2 - m^2}
\end{align}
for the full propagators one notices the same singularity as in eq. \eqref{eq:LSZ}. If one now compares the coefficients of these poles in eq. \eqref{eq:LSZ} one finds
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=2.0 pt, scale=1.3, arrow/.style={thick,->,shorten >=2pt,shorten <=2pt,>=stealth}]
	\node at (-4,0) {$\left\langle \left.\left.\vec{p}_1 \hdots \vec{p}_n \right| S \right| \vec{k}_1 \hdots \vec{k}_m \right\rangle =\sqrt{Z}^{n+m} \cdot$};
	\draw (0,0) circle (.75);
	\node at (0,0) {Amp.};

@@

This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}. Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine "Cuhre" which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}. The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
The computation of the real correction have been done by Wojciech Kotlarski, another member of the group. Comment on how real corrections are processed.\\

@@

	\node [block1a] at (-1,-1.5) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{V}|^2}$};

@@

	\node [block5b] at (7.5,-2.7) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ computation \newline of $ \sum |\mathcal{M}^{\mathrm{V}|^2}$ \newline \texttt{CUBA} $\to$ num. integration over $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$};

@@

\subsubsection{$K$-factors for Squark Production in the MSSM}
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
\end{center}
\end{figure}
Calculate uncertainties for multiple points(pdf, scale, integration)
\texttt{MadGraph5_aMC@NLO}\cite{Alwall:2014hca}
When generating the code for the process in question, e.g. two protons to $\tilde{u}_L + \tilde{u}_R$, with
\begin{lstlisting}
generate p p > ul ur [QCD] $$go
\end{lstlisting}
the $s$-channel gluinos were omitted as MadGraph does not deal with divergences coming from the gluino in the on-shell limit.

>>>>

Now considers the full $(n+m)$-point function in scalar theory. One can decompose it into an amputated $(n+m)$-point function and ``full'' propagators like written in eq. \eqref{eq:propagator} and depicted in fig. \ref{fig:fullpropagator}.

@@

	\draw[fill=black] (80:1.5) circle (.01);
	\draw[fill=black] (90:1.5) circle (.01);
	\draw[fill=black] (100:1.5) circle (.01);
	\draw[fill=black] (-80:1.5) circle (.01);
	\draw[fill=black] (-90:1.5) circle (.01);
	\draw[fill=black] (-100:1.5) circle (.01);
\end{tikzpicture}
\caption{Diagrammatic figure of a ``full' $(n+m)$-point function. Apart from the ``full'' propagators there is the ``full'' amputated $(n+m)$-point function}
\end{center}
\end{figure}\\
Inserting the expression
\begin{align}
\frac{i}{p^2 - m_0^2 - \Sigma(p^2)} \sim \frac{i Z}{p^2 - m^2}
\end{align}
for the full propagators one notices the same singularity as in eq. \eqref{eq:LSZ}. If one now compares the coefficients of these poles in eq. \eqref{eq:LSZ} one finds
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=2.0 pt, scale=1.3, arrow/.style={thick,->,shorten >=2pt,shorten <=2pt,>=stealth}]
	\node at (-4,0) {$\left\langle \left.\left.\vec{p}_1 \hdots \vec{p}_n \right| S \right| \vec{k}_1 \hdots \vec{k}_m \right\rangle =\sqrt{Z}^{n+m} \cdot$};
	\draw (0,0) circle (.75);
	\node at (0,0) {Amp.};

@@

This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}. Finally the phase space integration and the integration over $x_1$ and $x_2$ is performed by the integration routine ``Cuhre'' which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}. The parton density functions are included using \texttt{LHAPDF6}\cite{Buckley:2014ana}\\
The computation of the real correction has been done by Wojciech Kotlarski, another member of the group. Comment on how real corrections are processed.\\

@@

	\node [block1a] at (-1,-1.5) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$};

@@

	\node [block5b] at (7.5,-2.7) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ computation \newline of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ num. integration over $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$};

@@

\subsubsection{$K$-factors for Squark Production in the MSSM}
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msg=2000GeV.png}
\includegraphics[scale=.5]{figures/MSSM_uu_susu_Kfactors_msq=1000GeV.png}
\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$, where $\tilde{u}\tilde{u} \in \left\{ \tilde{u}_L\tilde{u}_R, \tilde{u}_L\tilde{u}_L, \tilde{u}_R\tilde{u}_R \right\}$, in the MSSM on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
\end{center}
\end{figure}
Calculate uncertainties for multiple points(pdf, scale, integration)
\texttt{MadGraph5\_aMC@NLO}\cite{Alwall:2014hca}
When generating the code for the process in question, e.g. two protons to $\tilde{u}_L + \tilde{u}_R$, with
\begin{lstlisting}[style=Mybash]
generate p p > ul ur [QCD] $$go
\end{lstlisting}
the $s$-channel gluinos were omitted as MadGraph does not deal with divergences coming from the gluino in the on-shell limit.
